Assessing Material Inventory Uncertainties in Integrated Fuel Cycle Simulations

### 2018-07-23 paper.tex
some corrections

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{Leniau2015125} which calculates the fissile fraction
required in the fuel to reach a given target burnup at the end of irradiation.
The targeted burnup is a operational parameter and does not necessary related to the
actual achieved burnup (computed from the real cycle length and the thermal
power of the reactor). Therefore, the uncertainty of the fuel enrichment is not
applied directly to the effective enrichment. It is instead applied to the
targeted burnup, resulting in a fuel enrichment uncertainty that is also close
to $10\%$.

For each of the parameters in Table \ref{tab:package_uncertainty}, a set of 199
simulations was performed with only that parameter being randomly varied.  An
additional set of 199 simulations was performed in which all five parameters are
randomly varied, using \gls{OFAT} method.  A reference simulation was performed
with all five parameters fixed at the mean value.

@@

The fuel enrichment contribution follow a close to constant uncertainty
contribution of $2\%$, so as the total relative uncertainty decrease, it has a
growing shared of the total absolute uncertainty over time.

@@

This preliminary study may suggest that the most important contributions to
natural uranium consumption and fissile inventory come from the parameters that
govern the exchange of material between facilities, and not from the physical
parameters that describe those facilities, such as thermal power or fuel
enrichment. Moreover such conclusions might change for different scenarios with
different hypothesis: not considering radioactive decay remove the decay of
$^{241}$Pu during cooling and considering a transition to fast reactors reduce
the effect of composition change induced by the cycle length variations.

@@

Finally, Figure \ref{fig:pu_uncer} shows the limit of the \gls{OFAT} method to
assess the individual contribution of each parameter, missing all the coupling
effects between each of them...

Cycle length impacts the discharge fuel burnup and the frequency of the fuel
loads.  When they combine to produce in uncertainty of the material
availability, this could result in variations related to time delays that may
contribute to the final uncertainty in ways that are not relevant to some
analyses.  That is, a simple time lag in a particular output that otherwise
follows an identical history could manifest itself as a large variation at any
particular time.  Those kind of time related uncertainties will require a
further analysis to understand and measure accurately their contributions to the
total uncertainty. I

@@

While the parameters contributing to natural uranium needs and fissile inventory
uncertainties might be obvious, such study allows to estimate each parameters
contribution, and it could be less obvious for other parameters, such as
plutonium quality, waste compositions.  Such studies could also provide research
guidance for nuclear archaeology work, which aims to precisely estimate past
fissile production by the different nuclear countries.

>>>>

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{Leniau2015125} which calculates the fissile fraction
required in the fuel to reach a given target burnup at the end of irradiation.
The target burnup is an operational parameter and does not necessary relate to
the actual achieved burnup (computed from the real cycle length and the thermal
power of the reactor). The uncertainty of the fuel enrichment is not applied
directly to the effective enrichment. It is instead applied to the targeted
burnup, resulting in a fuel enrichment uncertainty that is also close to $10\%$.

An set of 199 simulations was performed in which all five parameters are
randomly varied. Additionnaly, for each of the parameters in Table
\ref{tab:package_uncertainty}, a set of 199 simulations was performed with only
that parameter being randomly varied using the \gls{OFAT} method to estimated each
parameter contribution to the overall uncertianty.  A reference simulation was
performed with all five parameters fixed at the mean value.

@@

The fuel enrichment contribution follow a close to constant uncertainty
contribution of $2\%$, so as the total relative uncertainty decrease, it
has a growing share of the total absolute uncertainty over time.

@@

This preliminary study may suggest that the most important contributions to
natural uranium consumption and fissile inventory come from the parameters that
govern the exchange of material between facilities, and not from the physical
parameters that describe those facilities, such as thermal power or fuel
enrichment. Nevertheless such conclusions might constrained by the simulation
different hypothesis: not considering radioactive decay removes the decay of
$^{241}$Pu during cooling and considering a transition to fast reactors
minimizes the impact of the discharge composition change induced by the cycle
length variations.

@@

Finally, Figure \ref{fig:pu_uncer} shows the limit of the \gls{OFAT} method to
assess the individual contribution of each parameter, missing all the coupling
effects between them...

Cycle length impacts the discharge fuel burnup and the frequency of the fuel
loads.  When they combine to produce in uncertainty of the material
availability, this could result in variations related to time delays that may
contribute to the final uncertainty in ways that are not relevant to some
analyses.  That is, a simple time lag in a particular output that otherwise
follows an identical history could manifest itself as a large variation at any
particular time.  Those kind of time related uncertainties will require a
further analysis to understand and measure accurately their contributions to the
total uncertainty.

@@

Such studies could provide research guidance for nuclear archaeology work,
which aims to precisely estimate past fissile production by the different
nuclear countries.
